Methods and Results

### 2022-05-02 ms.Rmd
Adding in some model checks for potential outliers

###################
# Publication bias. Based on funnel plot, it looks like pub bias. Correct effect as a sensitivity analysis
###################

@@

  ###############
      # Harm type
  ################
  # Marginalised Harm type        
  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.4, cluster = data$study)

>>>>

        # Just some model checks
         checks = FALSE

         if(checks){
           hist(residuals(model1.1))

           cd.model1.1 <- cooks.distance(model1.1)
           plot(cd.model1.1, xlab = "Effect", ylab = "Cook's Distance")
           abline(h = 4/model1.1$k.all, col = "red", lty = 4)
        }
###################
# Publication bias. Based on funnel plot, it looks like pub bias. Correct effect as a sensitivity analysis
###################

@@

  # Just some model checks.
    if(checks){
           hist(residuals(model1.3))

           cd.model1.3 <- cooks.distance(model1.3)
           plot.cook(cd.model1.3, model1.3, "obs", data = data)
        }
  ###############
      # Harm type
  ################
  # Marginalised Harm type        
  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
  robust(model1.4, cluster = data$study)
